Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed some corrections.
Fixed typo.
Cosmetic changes.

We built the \Athena translator tool written in \Haskell
that generates \Agda proof-terms of \Metis derivations.
\Agda files delivered by this translator imports
\Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
We tested successful using this tool and \Agda as we
described in Section~\ref{sec:proof-reconstruction} over a subset of
propositional problems from~\cite{Prieto-Cubides2017}.

@@

One of the main contribution of this study was
increasing the trustworthiness of the automatic prover \Metis.
Justifying a proof by a theorem prover
has a real significant impact for these automatic tools.
The reverse engineering task to understand the prover reasoning
can reveal important issues or bugs
in many parts of these systems (\eg, preprocessing, reasoning, or
deduction modules). During this research, we had the opportunity
to contribute to \Metis by reporting some bugs\footnote{Issues No.~2,
No.~4. and commit \name{8a3f11e} in the \Metis' official repository
\url{https://github.com/gilith/metis}}.
Fortunately, all these problems were fixed quickly by
\citeauthor{hurd2003first} in the \Metis 20170810 release.

>>>>

We built the \Athena translator tool written in \Haskell
that generates \Agda proof-terms of \Metis derivations.
\Agda files generated by this translator imports
\Agda formalizations of the \Metis reasoning~\cite{AgdaProp,AgdaMetis}.
We tested successful using this tool and \Agda as we
described in Section~\ref{sec:proof-reconstruction} over a subset of
propositional problems from~\cite{Prieto-Cubides2017}.

@@

One of the main contribution of this study was increasing the
trustworthiness of the automatic prover \Metis.  Justifying a proof by
a theorem prover has a real significant impact for these automatic
tools.  The reverse engineering task to understand the prover
reasoning can reveal important issues or bugs in many parts of these
systems (\eg, preprocessing, reasoning, or deduction modules). During
this research, we had the opportunity to contribute to \Metis by
reporting some bugs---see Issues No.~2, No.~4. and commit
\name{8a3f11e} in \Metis' official
repository.\footnote{\url{https://github.com/gilith/metis}.}
Fortunately, all these problems were fixed quickly by
\citeauthor{hurd2003first} in \Metis~2.3 (release~20170822).
